Modeling the impacts of replacing car trips with combined public transport and cycling: \ Reproducible methods, results and actionable evidence from biclaR

### 2024-04-19 paper/PaperCEUS/PaperCEUS_rev1.Rmd
Shorten fig 2 caption

```{r jitter, fig.align='center', fig.cap="Representation of a flow-weighted random sample of 10,000 desire lines in the Lisbon metropolitan area between districts, without jittering (left) and with jittering (right).", out.width="100%"}

>>>>

```{r jitter, fig.align='center', fig.cap="Flow-weighted random sample of 10,000 desire lines in the Lisbon metropolitan area between districts, without jittering (left) and with jittering (right).", out.width="100%"}
